Ultrafast Electron Microscopes: Design Criteria, Electron Sources, and Column Modeling

### 2013-04-08 inc/photocathode/setup/setup.tex
tweak the introduction to photocathode engineering

%Sub-nanosecond (ultrafast) pulsed laser-driven electron sources are now being employed in a wide variety of scientific studies: in particular, ultrafast electron diffraction (UED) \cite{sciaini_femtosecond_2011}, ultrafast transmission electron microscopy (UEM)\cite{king_ultrafast_2005}, and pulsed X-ray free electron lasers \cite{dowell_cathode_2010}.
The spatial quality of the sources for UEM and UED are often characterized in terms of their normalized transverse rms emittance \cite{dowell_quantum_2009,jensen_emittance_2010}; $\varepsilon_{\smallT} = \Delta p_{\smallT} \Delta x / (m c)$, where $\Delta p_{\smallT} = \sqrt{ \langle p_{\smallT}^2 \rangle }$ is the rms transverse momentum of the source and $\Delta x = \sqrt{ \langle x^2 \rangle }$  is its size (cylindrical symmetry assumed), and $m$ is the electron rest mass and $c$ is the speed of light in vacuum.
This quantity is conserved under free-space propagation and perfect lensing, and may increase due to lens aberrations \cite{oshea_reversible_1998}.
As I have discussed in Chapter \ref{chap:considerations}, a electron beam (or in the case of UEM, a pulse) with a lower transverse emittance will result in higher quality images, however since this quantity is conserved, the only chance to minimize this quantity occurs upon emission.
As a reduction in the source size $\Delta x$ is limited either by the attainable diffraction-limited focusing or by the short-pulse Child's Law (screening of the electron gun's acceleration field) \cite{valfells_effects_2002}, significant improvements in the performance of scientific instruments employing pulsed electron sources through a reduction in their spatial emittance $\varepsilon_{\smallT}$ (and consequent increase in brightness \cite{berger_dc_2009}) may only be possible by decreasing the rms transverse momentum $\Delta p_{\smallT}$ of the electron source --- an intrinsic property of the emission source \cite{dowell_quantum_2009,jensen_emittance_2010}.

>>>>

%Sub-nanosecond (ultrafast) pulsed laser-driven electron sources are now being employed in a wide variety of scientific studies: in particular, ultrafast electron diffraction (UED) \cite{sciaini_femtosecond_2011}, ultrafast transmission electron microscopy (UEM)\cite{king_ultrafast_2005}, and pulsed X-ray free electron lasers \cite{dowell_cathode_2010}.
The spatial quality of the sources for UEM and UED are often characterized in terms of their normalized transverse rms emittance \cite{dowell_quantum_2009,jensen_emittance_2010}; $\varepsilon_{\smallT} = \Delta p_{\smallT} \Delta x / (m c)$, where $\Delta p_{\smallT} = \sqrt{ \langle p_{\smallT}^2 \rangle }$ is the rms transverse momentum of the source and $\Delta x = \sqrt{ \langle x^2 \rangle }$  is its size (cylindrical symmetry assumed), and $m$ is the electron rest mass and $c$ is the speed of light in vacuum.
This quantity is conserved under free-space propagation and perfect lensing, but may increase due to lens aberrations \cite{oshea_reversible_1998}.
As I have discussed in Chapter \ref{chap:considerations}, an electron beam (or in the case of UEM, a pulse) with a lower transverse emittance will result in higher quality images, however since this quantity is conserved, the only chance to minimize this quantity occurs upon emission.
As a reduction in the source size $\Delta x$ is limited either by the attainable diffraction-limited incident laser pulse focusing or by the short-pulse Child's Law (screening of the electron gun's acceleration field) \cite{valfells_effects_2002}, significant improvements in the performance of scientific instruments employing pulsed electron sources through a reduction in their spatial emittance $\varepsilon_{\smallT}$ (and consequent increase in brightness \cite{berger_dc_2009}) may only be possible by decreasing the rms transverse momentum $\Delta p_{\smallT}$ of the electron source --- an intrinsic property of the emission source \cite{dowell_quantum_2009,jensen_emittance_2010}.

To address this need, I have experimented with several candidate photocathodes, which belong to several different categories of photoemission processes.
In this chapter, I will present an example of each of these different processes, and discuss its prospects for reducing the transverse emittance and therefore utility as an electron source for UEM.
